Conservation decision-making under long transients

### 2019-08-02 slides/boettiger.Rmd
slides material

---
title: "Conservation decision-making under long transients"
author: "Carl Boettiger"
institute: "UC Berkeley"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

```{r echo=FALSE}
data %>% ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white") + 
  geom_line(data = det, lwd=2, color = "white")
```

@@

```{r echo=FALSE}
data %>% 
  ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white") + 
  geom_line(data = mean, lwd=2, color = rgb(.6, .6, 1))
```

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .6), rgba(50, 50, 50, .9)), url(img/royalsociety/gentoo-penguin.jpg)
background-size: 120%
class: center, top, inverse

>>>>

---
title: "Conservation decision-making under long transients"
author: "Carl Boettiger"
institute: "UC Berkeley"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"

---

@@

```{r echo=FALSE}
data %>% ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white") + 
  geom_line(data = mean, lwd=2, color = "white")
```

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .8), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin-wtf.jpg)
background-size: 120%
class: center, top, inverse
background-position: center

@@

```{r echo=FALSE}
data %>% 
  ggplot(aes(t,x, group=reps)) + 
  geom_line(alpha=0.02, color = "white") + 
  geom_line(data = mean, lwd = 2, color = "white") +
  geom_line(data = det, lwd = 2, color = rgb(.6, .6, 1)) 
```

@@

# Descision Theory
